Energy Regulation for Biologically-Inspired Robotics

### 2021-09-20 latex/nserc/proposal.tex
Wrote a better intro for the proposal based on darby's advice

%---------- Title -----------%
\title{Energy Regulation for Biologically-inspired Robotics}
\author{}
\date{}
\maketitle

\vspace{-1cm} % Move the following text up
%\textbf{What is your area of research? What sort of problems do you want to
%    address? WHy is the area important, and why are the applications important?
%    What is special about your approach, and how is it different from
%    existing/competing approaches? What is a sample application of the outcomes
%of your thesis?}
%\textbf{Detailed but concise. Provide background to position your research
%    within current knowledge of the field. State significance of research to the
%    field. Outline approach to be taken (citing literature). Clearly state
%differences btwn masters and this work.}

%---------- Main Content ----------%
\begin{large}
\textbf{Background}
\end{large}

When a gymnast wants to do backflips around a horizontal bar, they start by
performing a technique called a ``giant" \cite{usagym_giant}. 
The gymnast swings their legs based on their current speed and position, thereby
generating enough momentum to rotate around the bar.

@@

@@

Virtual constraints have proven useful for generating biologically-realistic
behaviour in robotic systems.
In my master's thesis I showed that VNHCs also allow for 
\textit{energy regulation}, i.e., they can inject energy into (or dissipate
energy from) a certain class of mechanical systems \cite{my-thesis}.
One such mechanical system is a gymnastics robot called the
\textit{acrobot}, for which I designed a VNHC that generates giant-like motion. 
This VNHC enables the acrobot to gain energy and perform backflips on a
horizontal bar.

@@

The advancements in mathematics from this research will bring improvements
to the control of all autonomous systems. 
The ability to safely transition between complex constraints by adding or
removing energy will allow for more expressive motion, and may become a standard
technique for controlling biologically inspired robots.

>>>>

%---------- Title -----------%
\title{Energy Regulation for Biologically-Inspired Robotics}
\author{}
\date{}
\maketitle

\vspace{-1.2cm} % Move the following text up
%\textbf{What is your area of research? What sort of problems do you want to
%    address? WHy is the area important, and why are the applications important?
%    What is special about your approach, and how is it different from
%    existing/competing approaches? What is a sample application of the outcomes
%of your thesis?}
%\textbf{Detailed but concise. Provide background to position your research
%    within current knowledge of the field. State significance of research to the
%    field. Outline approach to be taken (citing literature). Clearly state
%differences btwn masters and this work.}

%---------- Main Content ----------%
A robotic monkey swings through trees in a Mexican jungle, capturing valuable
wildlife data without disturbing the local environment. 
In the nearby city, a robotic police dog runs through the streets, weaving through
pedestrians' legs to catch a thief.
It passes a traveling circus group, where robot gymnasts perform elaborate
routines in front of an awestruck audience.
This world sounds like science fiction, but it is truly within sight;
our research will enable roboticists to accurately recreate human and animal
behaviour in their robots.
The future we imagined will become a present-day reality.

\begin{large}
\textbf{Background}
\end{large}

Before can explain how these humanoid and animal-like robots will work, we
must first understand how humans and animals move. 
Take the example of a human gymnast who  wants to do backflips around a
horizontal bar. 
The gymnast starts by swinging their legs based on their current speed and
position in a technique called a ``giant" \cite{usagym_giant}. 
This allows them to generate enough momentum to rotate around the bar.

@@

\newpage

@@

Virtual constraints have proven useful for generating biologically realistic
behaviour in robotic systems.
In my master's thesis I showed that VNHCs also allow for 
\textit{energy regulation}, i.e., they can inject energy into (or dissipate
energy from) a certain class of mechanical systems \cite{my-thesis}.
One such mechanical system is a gymnastics robot called the
\textit{acrobot}, for which I designed a VNHC that generates giant-like motion. 
This VNHC enables the acrobot to gain energy and perform backflips on a
horizontal bar.

@@

The advancements in mathematics from this research will bring improvements
to the control of all autonomous systems. 
The ability to safely transition between complex constraints by adding or
removing energy will allow for more expressive motion, and may become a standard
technique for controlling biologically-inspired robots.
